---
title: "Credit Card Profitability Analysis"
author: "Patricia Yin"
date: "09/02/2021"
output: html_document
---

```{r  echo=FALSE}
library(ggplot2)
library(glmnet)
library(tidyverse)
library(randomForest)
library(ROCR)
```

# I. Exploratory Data Analysis

## 1.1 Data cleaning and prepocessing

### prepare predicting variables:

```{r}
tag <- read.csv("data/train_tag.csv")
#recognise categorical variables
tag[c(2,3,5,6,7,8,10,11,12,13,14,15,16,18,30,35,37)] <- lapply(tag[c(2,3,5,6,7,8,10,11,12,13,14,15,16,18,30,35,37)], as.factor)

#remove level -1 in some categorical variables which only have a few entries
hist(tag$cur_credit_min_opn_dt_cnt)
summary(tag$cur_credit_cnt)
dat1 <- subset(tag, cur_credit_min_opn_dt_cnt != -1 & hld_crd_card_grd_cd != -1 & perm_crd_lmt_cd != -1)

#check frs_agn_dt_cnt because of too many empty values
dat1 <- subset(dat1, select = - frs_agn_dt_cnt)

#convert some continuous variables to be categorical according to their meanings
dat1$fin_rsk_ases_grd_cd <- as.factor(dat1$fin_rsk_ases_grd_cd)
dat1$confirm_rsk_ases_lvl_typ_cd <- as.factor(dat1$confirm_rsk_ases_lvl_typ_cd)
dat1$tot_ast_lvl_cd <- as.factor(dat1$tot_ast_lvl_cd)
dat1$pot_ast_lvl_cd <- as.factor(dat1$pot_ast_lvl_cd)

#code "" levels as "-1" indicating missing values
levels(tag$atdd_type) <- c("-1", "-1", "0", "1")
levels(tag$deg_cd) <- c("-1",  "~", "A", "B", "C", "D", "E", "Z")
levels(tag$edu_deg_cd) <- c("-1",  "~", "A", "B", "C", "D", "E", "F", "G", "J", "K", "L", "M", "Z")
```


### investigate highly skewed variables

```{r}
#investigate some outliers in variables
which.max(dat.t$cur_credit_cnt) #143
dat.t[143,]
which.max(dat.t$his_lng_ovd_day) #298
dat.t[298,]

#investigate the highly skewed variables
skew.df <- subset(dat.t, select = c(bk1_cur_year_mon_avg_agn_amt_cd, l12mon_buy_fin_mng_whl_tms, 
                                    l12_mon_fnd_buy_whl_tms, l12_mon_insu_buy_whl_tms, l12_mon_gld_buy_whl_tms,
                                    pl_crd_lmt_cd, good))

#try to combine adjacent levels with similar Weight of Evidence
check_woe <- function(var) {
  tab.var <- table(as.factor(var), good)
  df.var <- as.data.frame.matrix(tab.var)
  df.prop.var <- as.data.frame.matrix(prop.table(tab.var, 1))
  df.var$woe <- log(df.prop.var$"1" / df.prop.var$"0")
  return(df.var)
}

attach(skew.df)
check_woe(bk1_cur_year_mon_avg_agn_amt_cd)
check_woe(l12mon_buy_fin_mng_whl_tms)
check_woe(l12_mon_fnd_buy_whl_tms)
check_woe(l12_mon_insu_buy_whl_tms)#too few people buy insurance （8 people buy once)
check_woe(l12_mon_gld_buy_whl_tms)#too few people buy gold (5 people buy >= 1 time)
check_woe(pl_crd_lmt_cd)
detach()
```

No actions are taken to combine levels with similar WOE because too few people in certain levels.

### modify response variable:

```{r}
#response variable
hist(tag$ovd_30d_loan_tot_cnt)
#default for loan + credit card 
hist(tag$his_lng_ovd_day)
length(which(tag$his_lng_ovd_day != 0))
#default for credit card (customers without loan)
hist(tag$his_lng_ovd_day[tag$loan_act_ind==0])

#try to exclude customers with loan
dat1.1 <- dat1[dat1$loan_act_ind==0,]
length(which(dat1.1$his_lng_ovd_day > 0)) #only 3
length(which(dat1.1$ovd_30d_loan_tot_cnt > 0)) #only 1 person

#define Good as customers who never default
dat1$good <- ifelse(dat1$his_lng_ovd_day == 0, 1, 0) #Good as 1, Bad as 0
```

The dataset does not specify whether the default is on credit card or other loans. To deal with this, we attempted to remove all users who have other forms of loans so that only credit card users remained in the dataset and the default variable would only reflect users who have defaulted on credit card before. However, this reduced the size of our dataset significantly. The Bad accounts were reduced to 1. Thus, we decided to generalise our definition of a Bad account to be a user who have defaulted on any kind of loan before. 

### finalise dataset for modelling

```{r}
#investigate mrg_situ_cd
ggplot(dat1, aes(x=mrg_situ_cd, y=age)) + geom_boxplot()
attach(dat1)
mean(age[mrg_situ_cd=="A" & gdr_cd == "M"])
mean(age[mrg_situ_cd=="B" & gdr_cd == "M"])
detach()
#assume A = single, B = married

#subset our target group
dat.t <- subset(dat1, age<=35 & gdr_cd=="F" & mrg_situ_cd=="B", select = -c(age, gdr_cd, mrg_situ_cd))
#drop levels
dat.t <- droplevels(dat.t)

#select variables which reflect customer background and behaviour
dat.tf <- subset(dat.t, select = c(cur_debit_cnt, cur_credit_cnt, cur_debit_min_opn_dt_cnt, cur_credit_min_opn_dt_cnt, cur_debit_crd_lvl, hld_crd_card_grd_cd, crd_card_act_ind, l1y_crd_card_csm_amt_dlm_cd, atdd_type, perm_crd_lmt_cd, acdm_deg_cd, job_year, ic_ind, fr_or_sh_ind,
dnl_bind_cmb_lif_ind,
hav_car_grp_ind,
hav_hou_grp_ind,
l6mon_daim_aum_cd,
tot_ast_lvl_cd,
pot_ast_lvl_cd,
l12mon_buy_fin_mng_whl_tms,
l12_mon_fnd_buy_whl_tms,
l12_mon_insu_buy_whl_tms,
l12_mon_gld_buy_whl_tms,
loan_act_ind,
pl_crd_lmt_cd,
good))
```

edu_deg_cd, acdm_deg_cd, deg_cd are similar ideas. pick acdm_deg_cd because it has fewer levels than edu_deg_cd and more even distribution than deg_cd


## 1.2 Target group analysis

```{r}
summary(dat.tf)

#compare characteristics with the main group
summary(tag$dnl_mbl_bnk_ind) #99.96%
summary(tag$dnl_bind_cmb_lif_ind) #83.61%
summary(tag$crd_card_act_ind) #84.765%
```

Some conclusions can be drawn from this summary:

- our target group is very active in digital banking: they have all downloaded the bank's app (variable dnl_mbl_bnk_ind), 90.5% of them have downloaded the special app for credit card (variable dnl_bind_cmb_lif_ind)

- 85.9% of them are active credit card users (indicated by the variable crd_card_act_ind). However, only 16.4% of them have loans with CMB.

- 3.85% of them have defaulted, much smaller than the proportion that defaulted in the overall dataset (7.57%)

# II. From Initial to Final Model

## 2.1 Default risk

### glm model

```{r}
#raw model
glm.full <- glm(good~., data=dat.tf, family="binomial")
summary(glm.full)
glm.prob <- predict(glm.full, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

# remove non significant variables one by one
glm.1 <- glm(good~ .-pot_ast_lvl_cd, data=dat.tf, family="binomial")
summary(glm.1)
glm.prob <- predict(glm.1, type="response")
tab.1 <- table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)


glm.2 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms, data=dat.tf, family="binomial")
summary(glm.2)
glm.prob <- predict(glm.1, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.3 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms, data=dat.tf, family="binomial")
summary(glm.3)
glm.prob <- predict(glm.3, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.4 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind, data=dat.tf, family="binomial")
summary(glm.4)
glm.prob <- predict(glm.4, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.5 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd, data=dat.tf, family="binomial")
summary(glm.5)
glm.prob <- predict(glm.5, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.6 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt, data=dat.tf, family="binomial")
summary(glm.6)
glm.prob <- predict(glm.6, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.6 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt, data=dat.tf, family="binomial")
summary(glm.6)
glm.prob <- predict(glm.6, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)


glm.7 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind , data=dat.tf, family="binomial")
summary(glm.7)
glm.prob <- predict(glm.7, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.8 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind, data=dat.tf, family="binomial")
summary(glm.8)
glm.prob <- predict(glm.8, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.9 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt, data=dat.tf, family="binomial")
summary(glm.9)
glm.prob <- predict(glm.9, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.10 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year, data=dat.tf, family="binomial")
summary(glm.10)
glm.prob <- predict(glm.10, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.11 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind, data=dat.tf, family="binomial")
summary(glm.11)
glm.prob <- predict(glm.11, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)


glm.12 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl, data=dat.tf, family="binomial")
summary(glm.12)
glm.prob <- predict(glm.12, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.13 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl - cur_credit_cnt, data=dat.tf, family="binomial")
summary(glm.13)
glm.prob <- predict(glm.13, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)
 
glm.14 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl - cur_credit_cnt - hav_hou_grp_ind, data=dat.tf, family="binomial")
summary(glm.14)
glm.prob <- predict(glm.14, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.15 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl - cur_credit_cnt - hav_hou_grp_ind - l6mon_daim_aum_cd, data=dat.tf, family="binomial")
summary(glm.15)
glm.prob <- predict(glm.15, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.16 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl - cur_credit_cnt - hav_hou_grp_ind - l6mon_daim_aum_cd - hav_car_grp_ind, data=dat.tf, family="binomial")
summary(glm.16)
glm.prob <- predict(glm.16, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.17 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl - cur_credit_cnt - hav_hou_grp_ind - l6mon_daim_aum_cd - hav_car_grp_ind - cur_debit_cnt, data=dat.tf, family="binomial")
summary(glm.17)
glm.prob <- predict(glm.17, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.18 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl - cur_credit_cnt - hav_hou_grp_ind - l6mon_daim_aum_cd - hav_car_grp_ind - cur_debit_cnt - hld_crd_card_grd_cd, data=dat.tf, family="binomial")
summary(glm.18)
glm.prob <- predict(glm.18, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)
```

### glm performance

```{r}
# glm final model
glm.f <- glm(good ~ l1y_crd_card_csm_amt_dlm_cd + atdd_type + acdm_deg_cd + ic_ind + tot_ast_lvl_cd + l12mon_buy_fin_mng_whl_tms + l12_mon_fnd_buy_whl_tms + pl_crd_lmt_cd, data=dat.tf, family="binomial")
summary(glm.f)
glm.f.prob <- predict(glm.f, type="response")
table(ifelse(glm.f.prob>0.5, 1, 0), dat.tf$good)

prediction.glm <- prediction(glm.f.prob, dat.tf$good)
roc.glm <- performance(prediction.glm, measure="tpr", x.measure="fpr")
plot(roc.glm, lwd=2, colorkey=T, colorize=T, main="ROC curve - Logistic")
auc.glm <- performance(prediction.glm, "auc")
auc.glm <- as.numeric(auc.glm@y.values)
```

### random forest model 

```{r}
# Random Forest
set.seed(100)
rf.pop <- randomForest(as.factor(good) ~., data=dat.tf, mtry=5, importance=T)
importance(rf.pop)
varImpPlot(rf.pop, col=c("blue", "red"))

rf.prob <- predict(rf.pop, dat.tf, type="prob")[,2]

prediction.rf <- prediction(rf.prob, dat.tf$good)
roc.rf <- performance(prediction.rf, measure="tpr", x.measure="fpr")
plot(roc.rf, lwd=2, colorkey=T, colorize=T, main="ROC curve - Random Forest")
auc.rf <- performance(prediction.rf, "auc")
auc.rf <- as.numeric(auc.rf@y.values)
```

### random forest performance 

```{r}
#test performance of random forest through cross validation
dat_test.tf <- read.csv("data/test_tag_cleaned.csv")  #the test dataset has gone through the above cleaning process

#test performance of random forest on test data
rf.prob_test <- predict(rf.pop, dat_test.tf, type="prob")[,2]
prediction.rf_test <- prediction(rf.prob_test, dat_test.tf$good)
roc.rf_test <- performance(prediction.rf_test, measure="tpr", x.measure="fpr")
plot(roc.rf_test, lwd=2, colorkey=T, colorize=T, main="ROC curve - Random Forest on Testing Data")
auc.rf_test <- performance(prediction.rf_test, "auc")
auc.rf_test <- as.numeric(auc.rf_test@y.values)
```

## 2.2 Profitability 

We gathered the following statistics,

- merchant  service charge, m = 0.8%
  - policy paper "中国银联入网机构银行卡跨行交易收益分配办法"
- interest rate charged per billing period, r0 = 1.5%
  - common practice among chinese banks
- interest rate at which lender can borrow money each period, r_f = 0.2%
  - convert annualised interest rate for one-year treasury bonds to monthly interest rate
- percentage final loss of balance at default on credit card, l_d =  70%
  - according to Bank of China annual report "2019 年资本充足率报告" 
- average purchase per period using credit card, P = 590
  - calculated based on figures ("total amount of loans from credit card" + "no. of circulating cards") from CMB's annual report 2019
- average repayment per period, C = 637
  - calculated based on "profits from interest" + "total amount of loans from credit card" + "no. of circulating cards" from CMB's annual report
- average balance per period, B = 3147
  - calculated based on the assumption rB + P = C
  
```{r}
#assumptions
m = 0.8/100
r0 = 18.25/12/100
r_F = 0.2/100
l_D = 70/100
P = 590
C = 637
B = 3147
N = (B+C)/C #assume this to be constant when P changes
```


```{r}
#present equation of expected profitability from 
ind_exp_prof  <- function (r, p, P) {
  P*(m-1) + P*(1+r)^(N-1)*((1 - l_D + l_D * p^N)/((1+r_F)^N))
}

avg_prof <- function (r, p_list, P) {
  e_list = c()
  p_opt <- ((1-m) * (1+r_F)^N / (l_D * (1+r)^(N-1)) + (l_D-1)/l_D)^(1/N)
  for (i in p_list) {
    if (i > p_opt) {
      e_r <- ind_exp_prof(r, i, P)
      e_list <- c(e_list, e_r)
    }
  }
 return(mean(e_list))
}

# calculate current level of expected profitability of a potential customer
avg_prof(r=r0, p_list=rf.prob, P=590) #39.4543
```


```{r}
# generate a graph for relationship between interest rate and consumption level
r_seq <- seq(r1, r0, length.out=500)
P_seq <- rep(0, 500)
for (i in 1:500) {
  r = r_seq[i]
  for (perc in 0:600) {
    if (abs(avg_prof(r, rf.prob, 590*(1 + perc/1000)) - 39.45) <= 0.1) {
      P_seq[i] <- 590*(1 + perc/1000)
      break
    }
  }
}

r_seq.plot <- c()
P_seq.plot <- c()
for (i in 1:500) {
  if (P_seq[i] != 0) {
    r_seq.plot <- c(r_seq.plot, r_seq[i])
    P_seq.plot <- c(P_seq.plot, P_seq[i])
  }
}
plot(x=r_seq.plot * 12 * 100, y=P_seq.plot * 12, type="l", xlab="annualised interest rate, %", ylab="yearly consumption")
```
