---
title: "train_tag"
author: "Patricia Yin"
date: "09/02/2021"
output: html_document
---

```{r  echo=FALSE}
library(ggplot2)
library(glmnet)
library(tidyverse)
library(randomForest)
library(ROCR)
```


# I. Exploratory Data Analysis

load and view train_tag.csv dataset provided by a Chinese bank in a modelling competition.

```{r}
tag <- read.csv("../data/train_tag.csv")
dim(tag)[1]
colnames(tag)
rdm.index <- sample(dim(tag)[1], size=6)
tag[rdm.index,]
summary(tag)
```

## 1.1 Data cleaning and prepocessing

```{r}
#put categorical variables as fators
tag[c(2,3,5,6,7,8,10,11,12,13,14,15,16,18,30,35,37)] <- lapply(tag[c(2,3,5,6,7,8,10,11,12,13,14,15,16,18,30,35,37)], as.factor)
```

columns with -1:
frs_agn_dt_cnt, fin_rsk_ases_grd_cd, confirm_rsk_ases_lvl_typ_cd, tot_ast_lvl_cd,   pot_ast_lvl_cd, hld_crd_card_grd_cd, perm_crd_lmt_cd,  cur_credit_min_opn_dt_cnt

Treat them as missing values and remove rows with -1 in any columns from the dataset

```{r}
#try to remove -1
colnames(tag)
neg_col_index <- c(17, 19, 20, 23, 24, 34, 38, 42)
dat <- tag
for (i in 1:8) {
  dat <- subset(dat, dat[neg_col_index[i]] != -1)
}

dim(dat) 
dim(tag)
```

The reduced dataset is only 1/10 of the original one. Try to investigate why -1 was coded

```{r}
#check cur_credit_min_opn_dt_cnt
hist(tag$cur_credit_min_opn_dt_cnt)
summary(tag$cur_credit_cnt)
#remove rows with -1 in cur_credit_min_opn_dt_cnt
dat1 <- subset(tag, cur_credit_min_opn_dt_cnt != -1)

#check hld_crd_card_grd_cd
hist(tag$hld_crd_card_grd_cd)
#remove -1 in hld_crd_card_grd_cd
dat1 <- subset(dat1, hld_crd_card_grd_cd != -1)

#check perm_crd_lmt_cd
hist(tag$perm_crd_lmt_cd)
#remove -1 in perm_crd_lmt_cd
dat1 <- subset(dat1, perm_crd_lmt_cd != -1)

#check frs_agn_dt_cnt
hist(tag$frs_agn_dt_cnt)
summary(tag$l6mon_agn_ind)
length(which(tag$frs_agn_dt_cnt == -1)) #=18588
length(which(tag$frs_agn_dt_cnt == -1 & tag$l6mon_agn_ind == 0)) #=18528
#remove frs_agn_dt_cnt
dat1 <- subset(dat1, select = - frs_agn_dt_cnt)

#check fin_rsk_ases_grd_cd
hist(tag$fin_rsk_ases_grd_cd)
#code the variable as a factor
dat1$fin_rsk_ases_grd_cd <- as.factor(dat1$fin_rsk_ases_grd_cd)

#check confirm_rsk_ases_lvl_typ_cd
hist(tag$confirm_rsk_ases_lvl_typ_cd)
#code the variable as a factor
dat1$confirm_rsk_ases_lvl_typ_cd <- as.factor(dat1$confirm_rsk_ases_lvl_typ_cd)

#check tot_ast_lvl_cd
hist(tag$tot_ast_lvl_cd)
#code the variable as a factor
dat1$tot_ast_lvl_cd <- as.factor(dat1$tot_ast_lvl_cd)

#check pot_ast_lvl_cd
hist(tag$pot_ast_lvl_cd)
#code the variable as a factor
dat1$pot_ast_lvl_cd <- as.factor(dat1$pot_ast_lvl_cd)

#code "" levels as "-1"
levels(tag$atdd_type) <- c("-1", "-1", "0", "1")
levels(tag$deg_cd) <- c("-1",  "~", "A", "B", "C", "D", "E", "Z")
levels(tag$edu_deg_cd) <- c("-1",  "~", "A", "B", "C", "D", "E", "F", "G", "J", "K", "L", "M", "Z")
```

modify response variable:

```{r}
#response variable
hist(tag$ovd_30d_loan_tot_cnt)
#default for loan + credit card 
hist(tag$his_lng_ovd_day)
length(which(tag$his_lng_ovd_day != 0))
#default for credit card (customers without loan)
hist(tag$his_lng_ovd_day[tag$loan_act_ind==0])

#try to exclude customers with loan
dat1.1 <- dat1[dat1$loan_act_ind==0,]
length(which(dat1.1$his_lng_ovd_day > 0)) #only 3
length(which(dat1.1$ovd_30d_loan_tot_cnt > 0)) #only 1 person

#define Good as customers who never default
dat1$good <- ifelse(dat1$his_lng_ovd_day == 0, 1, 0) #Good as 1, Bad as 0
```
identify our target group: married women under 35

```{r}
#investigate mrg_situ_cd
ggplot(dat1, aes(x=mrg_situ_cd, y=age)) + geom_boxplot()
attach(dat1)
mean(age[mrg_situ_cd=="A" & gdr_cd == "M"])
mean(age[mrg_situ_cd=="B" & gdr_cd == "M"])
detach()
#assume A = single, B = married

#subset our target group
dat.t <- subset(dat1, age<=35 & gdr_cd=="F" & mrg_situ_cd=="B", select = -c(age, gdr_cd, mrg_situ_cd))
dim(dat.t)
summary(dat.t)

#compare characteristics with the main group
summary(tag$dnl_mbl_bnk_ind) #99.96%
summary(tag$dnl_bind_cmb_lif_ind) #83.61%
summary(tag$crd_card_act_ind) #84.765%
```

Some conclusions can be drawn from this summary:

- our target group is very active in digital banking: they have all downloaded the bank's app (variable dnl_mbl_bnk_ind), 90.5% of them have downloaded the special app for credit card (variable dnl_bind_cmb_lif_ind)

- 85.9% of them are active credit card users (indicated by the variable crd_card_act_ind). However, only 16.4% of them have loans with CMB.

- 3.85% of them have defaulted, much smaller than the proportion that defaulted in the overall dataset (7.57%)

Some variables are highly skewed

- bk1_cur_year_mon_avg_agn_amt_cd
- l12mon_buy_fin_mng_whl_tms
- l12_mon_fnd_buy_whl_tms
- l12_mon_insu_buy_whl_tms
- l12_mon_gld_buy_whl_tms

```{r}
#investigate some outliers in variables
which.max(dat.t$cur_credit_cnt) #143
dat.t[143,]
which.max(dat.t$his_lng_ovd_day) #298
dat.t[298,]

#investigate the highly skewed variables
skew.df <- subset(dat.t, select = c(bk1_cur_year_mon_avg_agn_amt_cd, l12mon_buy_fin_mng_whl_tms, 
                                    l12_mon_fnd_buy_whl_tms, l12_mon_insu_buy_whl_tms, l12_mon_gld_buy_whl_tms,
                                    pl_crd_lmt_cd, good))

#combine adjacent levels with similar Weight of Evidence
check_woe <- function(var) {
  tab.var <- table(as.factor(var), good)
  df.var <- as.data.frame.matrix(tab.var)
  df.prop.var <- as.data.frame.matrix(prop.table(tab.var, 1))
  df.var$woe <- log(df.prop.var$"1" / df.prop.var$"0")
  return(df.var)
}

attach(skew.df)
check_woe(bk1_cur_year_mon_avg_agn_amt_cd)

check_woe(l12mon_buy_fin_mng_whl_tms)

check_woe(l12_mon_fnd_buy_whl_tms)

check_woe(l12_mon_insu_buy_whl_tms)
#too few people buy insurance （8 people buy once)

check_woe(l12_mon_gld_buy_whl_tms)
#too few people buy gold (5 people buy >= 1 time)

check_woe(pl_crd_lmt_cd)
detach()
```


```{r}
#drop levels
dat.t <- droplevels(dat.t)

#select variables which reflect customer background and behaviour
dat.tf <- subset(dat.t, select = c(cur_debit_cnt, cur_credit_cnt, cur_debit_min_opn_dt_cnt, cur_credit_min_opn_dt_cnt, cur_debit_crd_lvl, hld_crd_card_grd_cd, crd_card_act_ind, l1y_crd_card_csm_amt_dlm_cd, atdd_type, perm_crd_lmt_cd, acdm_deg_cd, job_year, ic_ind, fr_or_sh_ind,
dnl_bind_cmb_lif_ind,
hav_car_grp_ind,
hav_hou_grp_ind,
l6mon_daim_aum_cd,
tot_ast_lvl_cd,
pot_ast_lvl_cd,
l12mon_buy_fin_mng_whl_tms,
l12_mon_fnd_buy_whl_tms,
l12_mon_insu_buy_whl_tms,
l12_mon_gld_buy_whl_tms,
loan_act_ind,
pl_crd_lmt_cd,
good))
```

edu_deg_cd, acdm_deg_cd, deg_cd are similar ideas. pick acdm_deg_cd because it has fewer levels than edu_deg_cd and more even distribution than deg_cd


II. From Initial to Final Model

```{r}
#raw model
glm.full <- glm(good~., data=dat.tf, family="binomial")
summary(glm.full)
glm.prob <- predict(glm.full, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

# remove variables one by one
glm.1 <- glm(good~ .-pot_ast_lvl_cd, data=dat.tf, family="binomial")
summary(glm.1)
glm.prob <- predict(glm.1, type="response")
tab.1 <- table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)


glm.2 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms, data=dat.tf, family="binomial")
summary(glm.2)
glm.prob <- predict(glm.1, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.3 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms, data=dat.tf, family="binomial")
summary(glm.3)
glm.prob <- predict(glm.3, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.4 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind, data=dat.tf, family="binomial")
summary(glm.4)
glm.prob <- predict(glm.4, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.5 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd, data=dat.tf, family="binomial")
summary(glm.5)
glm.prob <- predict(glm.5, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.6 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt, data=dat.tf, family="binomial")
summary(glm.6)
glm.prob <- predict(glm.6, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.6 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt, data=dat.tf, family="binomial")
summary(glm.6)
glm.prob <- predict(glm.6, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)


glm.7 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind , data=dat.tf, family="binomial")
summary(glm.7)
glm.prob <- predict(glm.7, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.8 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind, data=dat.tf, family="binomial")
summary(glm.8)
glm.prob <- predict(glm.8, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.9 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt, data=dat.tf, family="binomial")
summary(glm.9)
glm.prob <- predict(glm.9, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.10 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year, data=dat.tf, family="binomial")
summary(glm.10)
glm.prob <- predict(glm.10, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.11 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind, data=dat.tf, family="binomial")
summary(glm.11)
glm.prob <- predict(glm.11, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)


glm.12 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl, data=dat.tf, family="binomial")
summary(glm.12)
glm.prob <- predict(glm.12, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.13 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl - cur_credit_cnt, data=dat.tf, family="binomial")
summary(glm.13)
glm.prob <- predict(glm.13, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)
 
glm.14 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl - cur_credit_cnt - hav_hou_grp_ind, data=dat.tf, family="binomial")
summary(glm.14)
glm.prob <- predict(glm.14, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.15 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl - cur_credit_cnt - hav_hou_grp_ind - l6mon_daim_aum_cd, data=dat.tf, family="binomial")
summary(glm.15)
glm.prob <- predict(glm.15, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.16 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl - cur_credit_cnt - hav_hou_grp_ind - l6mon_daim_aum_cd - hav_car_grp_ind, data=dat.tf, family="binomial")
summary(glm.16)
glm.prob <- predict(glm.16, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.17 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl - cur_credit_cnt - hav_hou_grp_ind - l6mon_daim_aum_cd - hav_car_grp_ind - cur_debit_cnt, data=dat.tf, family="binomial")
summary(glm.17)
glm.prob <- predict(glm.17, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

glm.18 <- glm(good~ .-pot_ast_lvl_cd - l12_mon_gld_buy_whl_tms - l12_mon_insu_buy_whl_tms - loan_act_ind - perm_crd_lmt_cd - cur_debit_min_opn_dt_cnt - crd_card_act_ind - dnl_bind_cmb_lif_ind - cur_credit_min_opn_dt_cnt - job_year - fr_or_sh_ind - cur_debit_crd_lvl - cur_credit_cnt - hav_hou_grp_ind - l6mon_daim_aum_cd - hav_car_grp_ind - cur_debit_cnt - hld_crd_card_grd_cd, data=dat.tf, family="binomial")
summary(glm.18)
glm.prob <- predict(glm.18, type="response")
table(ifelse(glm.prob>0.5, 1, 0), dat.tf$good)

# glm final model
glm.f <- glm(good ~ l1y_crd_card_csm_amt_dlm_cd + atdd_type + acdm_deg_cd + ic_ind + tot_ast_lvl_cd + l12mon_buy_fin_mng_whl_tms + l12_mon_fnd_buy_whl_tms + pl_crd_lmt_cd, data=dat.tf, family="binomial")
summary(glm.f)
glm.f.prob <- predict(glm.f, type="response")
table(ifelse(glm.f.prob>0.5, 1, 0), dat.tf$good)

prediction.glm <- prediction(glm.f.prob, dat.tf$good)
roc.glm <- performance(prediction.glm, measure="tpr", x.measure="fpr")
plot(roc.glm, lwd=2, colorkey=T, colorize=T, main="ROC curve - Logistic")
auc.glm <- performance(prediction.glm, "auc")
auc.glm <- as.numeric(auc.glm@y.values)

# Random Forest
set.seed(100)
rf.pop <- randomForest(as.factor(good) ~., data=dat.tf, mtry=5, importance=T)
importance(rf.pop)
varImpPlot(rf.pop, col=c("blue", "red"))

rf.prob <- predict(rf.pop, dat.tf, type="prob")[,2]

prediction.rf <- prediction(rf.prob, dat.tf$good)
roc.rf <- performance(prediction.rf, measure="tpr", x.measure="fpr")
plot(roc.rf, lwd=2, colorkey=T, colorize=T, main="ROC curve - Random Forest")
auc.rf <- performance(prediction.rf, "auc")
auc.rf <- as.numeric(auc.rf@y.values)
```

```{r}
#test performance of random forest through cross validation
test.index <- sample(dim(dat.tf)[1], 185)
dat_test.tf <- dat.tf[test.index,]
dat_train.tf <- dat.tf[-test.index,]

set.seed(1000)
rf.pop <- randomForest(as.factor(good) ~., data=dat_train.tf, mtry=5, importance=T)

rf.prob_train <- predict(rf.pop, dat_train.tf, type="prob")[,2]
prediction.rf_train <- prediction(rf.prob_train, dat_train.tf$good)
roc.rf_train <- performance(prediction.rf_train, measure="tpr", x.measure="fpr")
plot(roc.rf_train, lwd=2, colorkey=T, colorize=T, main="ROC curve - Random Forest on Training Data")
auc.rf_train <- performance(prediction.rf_train, "auc")
auc.rf_train <- as.numeric(auc.rf_train@y.values)

#test performance of random forest on test data
rf.prob_test <- predict(rf.pop, dat_test.tf, type="prob")[,2]
prediction.rf_test <- prediction(rf.prob_test, dat_test.tf$good)
roc.rf_test <- performance(prediction.rf_test, measure="tpr", x.measure="fpr")
plot(roc.rf_test, lwd=2, colorkey=T, colorize=T, main="ROC curve - Random Forest on Testing Data")
auc.rf_test <- performance(prediction.rf_test, "auc")
auc.rf_test <- as.numeric(auc.rf_test@y.values)
```

We gathered the following statistics,

- merchant  service charge, m = 0.8%
  - policy paper "中国银联入网机构银行卡跨行交易收益分配办法"
- interest rate charged per billing period, r0 = 1.5%
  - common practice among chinese banks
- interest rate at which lender can borrow money each period, r_f = 0.2%
  - convert annualised interest rate for one-year treasury bonds to monthly interest rate
- percentage final loss of balance at default on credit card, l_d =  70%
  - according to Bank of China annual report "2019 年资本充足率报告" 
- average purchase per period using credit card, P = 590
  - calculated based on figures ("total amount of loans from credit card" + "no. of circulating cards") from CMB's annual report 2019
- average repayment per period, C = 637
  - calculated based on "profits from interest" + "total amount of loans from credit card" + "no. of circulating cards" from CMB's annual report
- average balance per period, B = 3147
  - calculated based on the assumption rB + P = C
  
```{r}
#assumptions
m = 0.8/100
r0 = 18.25/12/100
r_F = 0.2/100
l_D = 70/100
P = 590
C = 637
B = 3147
N = (B+C)/C #assume this to be constant when P changes
```

Set interest rate 

```{r}
#present equation of expected profitability from 
ind_exp_prof  <- function (r, p, P) {
  P*(m-1) + P*(1+r)^(N-1)*((1 - l_D + l_D * p^N)/((1+r_F)^N))
}

avg_prof <- function (r, p_list, P) {
  e_list = c()
  p_opt <- ((1-m) * (1+r_F)^N / (l_D * (1+r)^(N-1)) + (l_D-1)/l_D)^(1/N)
  for (i in p_list) {
    if (i > p_opt) {
      e_r <- ind_exp_prof(r, i, P)
      e_list <- c(e_list, e_r)
    }
  }
 return(mean(e_list))
}


avg_prof(r=r0, p_list=rf.prob, P=590) #39.4543

r1 = r0 * 0.7
avg_prof(r=r1, rf.prob, P=590*1.49) #39.52723
```


```{r}
# generate a better graph
r_seq <- seq(r1, r0, length.out=500)
P_seq <- rep(0, 500)
for (i in 1:500) {
  r = r_seq[i]
  for (perc in 0:600) {
    if (abs(avg_prof(r, rf.prob, 590*(1 + perc/1000)) - 39.45) <= 0.1) {
      P_seq[i] <- 590*(1 + perc/1000)
      break
    }
  }
}

r_seq.plot <- c()
P_seq.plot <- c()
for (i in 1:500) {
  if (P_seq[i] != 0) {
    r_seq.plot <- c(r_seq.plot, r_seq[i])
    P_seq.plot <- c(P_seq.plot, P_seq[i])
  }
}
plot(x=r_seq.plot * 12 * 100, y=P_seq.plot * 12, type="l", xlab="annualised interest rate, %", ylab="yearly consumption")


model.dat <- data.frame(cbind(12*100*r_seq.plot, 12*P_seq.plot))
model.dat[which.min(model.dat$X1),]
model.dat[250,]
```

```{r}

```

