---
title: "train_tag"
author: "Patricia Yin"
date: "09/02/2021"
output: html_document
---

# I. Exploratory Data Analysis

load and view train_tag.csv dataset provided by a Chinese bank in a modelling competition.

```{r}
library(tidyverse)
library(ggplot2)

tag <- read.csv("../data/train_tag.csv")
dim(tag)[1]
colnames(tag)
rdm.index <- sample(dim(tag)[1], size=6)
tag[rdm.index,]
summary(tag)
```

## 1.1 Data cleaning and prepocessing

```{r}
#put categorical variables as fators
tag[c(2,3,5,6,7,8,10,11,12,13,14,15,16,18,30,35,37)] <- lapply(tag[c(2,3,5,6,7,8,10,11,12,13,14,15,16,18,30,35,37)], as.factor)
```

columns with -1:
frs_agn_dt_cnt, fin_rsk_ases_grd_cd, confirm_rsk_ases_lvl_typ_cd, tot_ast_lvl_cd,   pot_ast_lvl_cd, hld_crd_card_grd_cd, perm_crd_lmt_cd,  cur_credit_min_opn_dt_cnt

Treat them as missing values and remove rows with -1 in any columns from the dataset

```{r}
#try to remove -1
colnames(tag)
neg_col_index <- c(17, 19, 20, 23, 24, 34, 38, 42)
dat <- tag
for (i in 1:8) {
  dat <- subset(dat, dat[neg_col_index[i]] != -1)
}

dim(dat) 
dim(tag)
```

The reduced dataset is only 1/10 of the original one. Try to investigate why -1 was coded

```{r}
#check cur_credit_min_opn_dt_cnt
hist(tag$cur_credit_min_opn_dt_cnt)
summary(tag$cur_credit_cnt)
#remove rows with -1 in cur_credit_min_opn_dt_cnt
dat1 <- subset(tag, cur_credit_min_opn_dt_cnt != -1)

#check hld_crd_card_grd_cd
hist(tag$hld_crd_card_grd_cd)
#remove -1 in hld_crd_card_grd_cd
dat1 <- subset(dat1, hld_crd_card_grd_cd != -1)

#check perm_crd_lmt_cd
hist(tag$perm_crd_lmt_cd)
#remove -1 in perm_crd_lmt_cd
dat1 <- subset(dat1, perm_crd_lmt_cd != -1)

#check frs_agn_dt_cnt
hist(tag$frs_agn_dt_cnt)
summary(tag$l6mon_agn_ind)
length(which(tag$frs_agn_dt_cnt == -1)) #=18588
length(which(tag$frs_agn_dt_cnt == -1 & tag$l6mon_agn_ind == 0)) #=18528
#remove frs_agn_dt_cnt
dat1 <- subset(dat1, select = - frs_agn_dt_cnt)

#check fin_rsk_ases_grd_cd
hist(tag$fin_rsk_ases_grd_cd)
#code the variable as a factor
dat1$fin_rsk_ases_grd_cd <- as.factor(dat1$fin_rsk_ases_grd_cd)

#check confirm_rsk_ases_lvl_typ_cd
hist(tag$confirm_rsk_ases_lvl_typ_cd)
#code the variable as a factor
dat1$confirm_rsk_ases_lvl_typ_cd <- as.factor(dat1$confirm_rsk_ases_lvl_typ_cd)

#check tot_ast_lvl_cd
hist(tag$tot_ast_lvl_cd)
#code the variable as a factor
dat1$tot_ast_lvl_cd <- as.factor(dat1$tot_ast_lvl_cd)

#check pot_ast_lvl_cd
hist(tag$pot_ast_lvl_cd)
#code the variable as a factor
dat1$pot_ast_lvl_cd <- as.factor(dat1$pot_ast_lvl_cd)

#code "" levels as "-1"
levels(tag$atdd_type) <- c("-1", "-1", "0", "1")
levels(tag$deg_cd) <- c("-1",  "~", "A", "B", "C", "D", "E", "Z")
levels(tag$edu_deg_cd) <- c("-1",  "~", "A", "B", "C", "D", "E", "F", "G", "J", "K", "L", "M", "Z")
```

modify response variable:

```{r}
#response variable
hist(tag$ovd_30d_loan_tot_cnt)
#default for loan + credit card 
hist(tag$his_lng_ovd_day)
length(which(tag$his_lng_ovd_day != 0))
#default for credit card (customers without loan)
hist(tag$his_lng_ovd_day[tag$loan_act_ind==0])

#try to exclude customers with loan
dat1.1 <- dat1[dat1$loan_act_ind==0,]
length(which(dat1.1$his_lng_ovd_day > 0)) #only 3
length(which(dat1.1$ovd_30d_loan_tot_cnt > 0)) #only 1 person

#define Good as customers who never default
dat1$good <- as.factor(ifelse(dat1$his_lng_ovd_day == 0, 1, 0)) #Good as 1, Bad as 0
summary(dat1$good)
```
identify our target group: married women under 35

```{r}
#investigate mrg_situ_cd
ggplot(dat1, aes(x=mrg_situ_cd, y=age)) + geom_boxplot()
attach(dat1)
mean(age[mrg_situ_cd=="A" & gdr_cd == "M"])
mean(age[mrg_situ_cd=="B" & gdr_cd == "M"])
detach()
#assume A = single, B = married

#subset our target group
dat.t <- subset(dat1, age<=35 & gdr_cd=="F" & mrg_situ_cd=="B", select = -c(age, gdr_cd, mrg_situ_cd))
dim(dat.t)
summary(dat.t)

```

Some conclusions can be drawn from this summary:

- our target group is very active in digital banking: they have all downloaded the bank's app (variable dnl_mbl_bnk_ind), 90.5% of them have downloaded the special app for credit card (variable dnl_bind_cmb_lif_ind)

- 85.9% of them are active credit card users (indicated by the variable crd_card_act_ind). However, only 16.4% of them have loans with CMB.

- 3.85% of them have defaulted, much smaller than the proportion that defaulted in the overall dataset (7.57%)

Some variables are highly skewed

- bk1_cur_year_mon_avg_agn_amt_cd
- l12mon_buy_fin_mng_whl_tms
- l12_mon_fnd_buy_whl_tms
- l12_mon_insu_buy_whl_tms
- l12_mon_gld_buy_whl_tms

```{r}
#investigate some outliers in variables
which.max(dat.t$cur_credit_cnt) #143
dat.t[143,]
which.max(dat.t$his_lng_ovd_day) #298
dat.t[298,]

#investigate the highly skewed variables
skew.df <- subset(dat.t, select = c(bk1_cur_year_mon_avg_agn_amt_cd, l12mon_buy_fin_mng_whl_tms, 
                                    l12_mon_fnd_buy_whl_tms, l12_mon_insu_buy_whl_tms, l12_mon_gld_buy_whl_tms,
                                    pl_crd_lmt_cd, good))

#combine adjacent levels with similar Weight of Evidence
check_woe <- function(var) {
  tab.var <- table(as.factor(var), good)
  df.var <- as.data.frame.matrix(tab.var)
  df.prop.var <- as.data.frame.matrix(prop.table(tab.var, 1))
  df.var$woe <- log(df.prop.var$"1" / df.prop.var$"0")
  return(df.var)
}

attach(skew.df)
check_woe(bk1_cur_year_mon_avg_agn_amt_cd)

check_woe(l12mon_buy_fin_mng_whl_tms)

check_woe(l12_mon_fnd_buy_whl_tms)

check_woe(l12_mon_insu_buy_whl_tms)
#too few people buy insurance （8 people buy once)

check_woe(l12_mon_gld_buy_whl_tms)
#too few people buy gold (5 people buy >= 1 time)

check_woe(pl_crd_lmt_cd)
detach()
```


```{r}
#drop levels
dat.t <- droplevels(dat.t)
summary(dat.t)

#select variables which reflect customer background and behaviour
dat.tf <- subset(dat.t, select = c(cur_debit_cnt, cur_credit_cnt, cur_debit_min_opn_dt_cnt, cur_credit_min_opn_dt_cnt, cur_debit_crd_lvl, hld_crd_card_grd_cd, crd_card_act_ind, l1y_crd_card_csm_amt_dlm_cd, atdd_type, perm_crd_lmt_cd, acdm_deg_cd, job_year, ic_ind, fr_or_sh_ind,
dnl_bind_cmb_lif_ind,
hav_car_grp_ind,
hav_hou_grp_ind,
l6mon_daim_aum_cd,
tot_ast_lvl_cd,
pot_ast_lvl_cd,
l12mon_buy_fin_mng_whl_tms,
l12_mon_fnd_buy_whl_tms,
l12_mon_insu_buy_whl_tms,
l12_mon_gld_buy_whl_tms,
loan_act_ind,
pl_crd_lmt_cd,
good))
summary(dat.tf)
```

edu_deg_cd, acdm_deg_cd, deg_cd are similar ideas. pick acdm_deg_cd because it has fewer levels than edu_deg_cd and more even distribution than deg_cd


II. From Initial to Final Model

```{r}
#raw model
glm.f <- glm(good~., data=dat.tf, family="binomial")
summary(glm.f)

#classification table
ct.op <- function(predicted, observed) {
  df.op <- data.frame(predicted = predicted, observed = observed)
  # create a table
  op.tab <- table(df.op)
  # use the prop.table function to obtain the rows we need and stack them on
  # top of each other with rbind
  op.tab <- rbind(op.tab, c(round(prop.table(op.tab, 2)[1, 1], 2), round((prop.table(op.tab,2)[2, 2]), 2)))
  # name the rows
  rownames(op.tab) <- c("pred=0", "pred=1", "%corr")
  # name the columns
  colnames(op.tab) <- c("obs=0", "obs=1")
  # return the table
  op.tab
}
ct.op(as.numeric(glm.f$fitted.values>0.5), dat.tf$good)

#automatic model selection by AIC
glm.n <- glm(good~1, data=dat.tf, family="binomial")

glm.fwd <- step(glm.n, scope = list(lower = glm.n, upper = glm.f), 
             direction = "forward", trace = 0)
ct.op(as.numeric(glm.fwd$fitted.values>0.5), dat.tf$good)

glm.bwd <- step(glm.f, direction = "backward", trace = 0)
summary(glm.bwd)
ct.op(as.numeric(glm.bwd$fitted.values>0.5), dat.tf$good)

glm.bi <- step(glm.f, direction = "both", trace = 0)
summary(glm.bi)
ct.op(as.numeric(glm.bi$fitted.values>0.5), dat.tf$good)
```

